Decoding UK Hospital Wait Times: Infrastructure, Workforce, and Demand

### 2024-11-24 paper/paper.qmd
Completed model file and imported model to main paper.

Understanding the drivers of wait times is vital for improving healthcare access and efficiency. By identifying the factors contributing to delays, this paper offers actionable insights for policymakers and healthcare administrators seeking to enhance patient outcomes and system resilience. The remainder of this paper is structured as follows: @sec-data details the data and methodology, @sec-model presents the model used for analysis of the data, @sec-results presents the key results from the model, and @sec-discussion concludes with final analysis of the results and recommendations for future research.

@@

## Measurement
**Physicians per 1,000** [@physicians]. Source: Physician counts are sourced from the OECD, relying on NHS Digital, Public Health Scotland, and the General Medical Council (GMC). The data reflect licensed physicians, encompassing both general practitioners and specialists. The metric is calculated as the total number of physicians per 1,000 population. The dataset includes both headcount and rolecount metrics, with post-2009 data transitioning to headcount for greater accuracy. Physician counts include GP retainers and full-time equivalents, providing an accurate picture of the available workforce. Historical data adjustments account for changes in collection methodologies. Similar datasets include WHO and Eurostat health statistics offer broader regional comparisons but lack the granularity needed for a UK-focused study.

@@

# Split the table into smaller parts
part1 <- cleaned_data[, 1:6]  
part2 <- cleaned_data[, 7:ncol(cleaned_data)]

@@

# Fit the linear regression model
model <- lm(
   Pct_Wait_Avg ~ beds_per_1000 + physicians_per_1000 + attendance,
  data = cleaned_data
)

# Display the model summary in a table
modelsummary::modelsummary(
  list("Linear Model" = model),
  statistic = c("p.value")
)

```

>>>>

Understanding the drivers of wait times is vital for improving healthcare access and efficiency [@king]. By identifying the factors contributing to delays, this paper offers actionable insights for policymakers and healthcare administrators seeking to enhance patient outcomes and system resilience. The remainder of this paper is structured as follows: @sec-data details the data and methodology, @sec-model presents the model used for analysis of the data, @sec-results presents the key results from the model, and @sec-discussion concludes with final analysis of the results and recommendations for future research.

@@

## Measurement
**Physicians per 1,000** [@physicians]. Physician counts are sourced from the OECD, relying on NHS Digital, Public Health Scotland, and the General Medical Council (GMC). The data reflect licensed physicians, encompassing both general practitioners and specialists. The metric is calculated as the total number of physicians per 1,000 population. The dataset includes both headcount and rolecount metrics, with post-2009 data transitioning to headcount for greater accuracy. Physician counts include GP retainers and full-time equivalents, providing an accurate picture of the available workforce. Historical data adjustments account for changes in collection methodologies. Similar datasets include WHO and Eurostat health statistics offer broader regional comparisons but lack the granularity needed for a UK-focused study.

@@

# Split the table into smaller parts
part1 <- cleaned_data[, 1:4]  
part2 <- cleaned_data[, 4:ncol(cleaned_data)]

@@

# Load the saved model
model <- readRDS("../models/wait_times_model.rds")

# Display the model summary in a table
modelsummary::modelsummary(
  list("Frequentist Linear Model" = model),
  statistic = c("p.value")
)
```
